### 2015-06-27 reports/paper/experiment.tex
thesis update

The volume of the acoustic source can also be used to control the color of the dots painted in the above experiment. For signal $x_i[n]$ received at each microphone $i$, the power $P_i$ can be used as an indicator of the source volume:
\[
P_i = \frac{1}{N} \sum_{i=1}^N x_i[i]^2
\]
Since there are $6$ microphones in our system ($3$ in each array), we choose the maximum power $P$ received across all $6$ microphones as the indicator for the source volume:
\[
P = \max_i P_i 
\]
However, the received power of the audio signal is itself a function of the audio source location (since the received power decays with increasing distance between the source to receiver). Therefore, the received power needs to be normalized. For the power $P$ received at location $(x,y)$, we normalize it by a scaling factor $b_{xy}$. The normalized power $\bar{P}$ is:

@@

>>>>

The volume of the acoustic source can also be used to control the color of the dots painted in the above experiment. For signal $x_i[n]$ received at each microphone $i$, the power $P_i$ can be used as an indicator of the source volume:
\[
P_i = \frac{1}{N} \sum_{i=1}^N x_i[i]^2
\]

Since there are $6$ microphones in our system ($3$ in each array), we choose the maximum power $P$ received across all $6$ microphones as the indicator for the source volume:
\[
P = \max_i P_i 
\]

However, the received power of the audio signal is itself a function of the audio source location (since the received power decays with increasing distance between the source to receiver). Therefore, the received power needs to be normalized. For the power $P$ received at location $(x,y)$, we normalize it by a scaling factor $b_{xy}$. The normalized power $\bar{P}$ is:

@@

\begin{figure}[h!]
  \centering
    \includegraphics[width=\textwidth]{color_5.png}
    \caption{Painting an eclipse. The color of the heart changes with the volume of the song.}
    \label{fig:show_color_3}
\end{figure}

\textcolor{red}{ Instead of stop and change the sound volume, we carried out a similar experiment where the volume is changed as we move the source. In this experiment, we drew an ellipse by free hand in a clockwise fashion. We started with the volume set to the maximum (which corresponds to the red color). Then we gradually decreases the volume as the move to the right. After the volume is decreased to $60\%$ of the maximum volume we started with, we start to gradually increase the volume until the maximum volume is reached again. Figure~\ref{fig:show_color_3} gives a visual presentation of the painted result. As can be seen from the figure, the color is red at the top left region of the ellipse. The color changes to the green yellow range and then back go red orange range as we completes the ellipse. A video demonstration of this experiment is available at~\cite{demo:color3} }

### 2015-06-27 reports/paper/simulation.tex
update
thesis update

To avoid the need to accurately place microphones at far distances (as required by fig~\ref{fig:sim_hm_4}), we explored configuration with two arrays. Two $3$ microphone array are placed $1$ meter apart and the result is presented in fig~\ref{fig:sim_hm_2_array}.  The result indicates that this configuration has good accuracy when source is close to the arrays. We observe that the localization accuracy decreases as the sound source moves outside of the region one meter by one meter away from the two arrays. The average error is $2.60$ cm.

@@

Looking at the simulation results on localization accuracy for different microphone array size and configurations, we see that the further away the microphones are placed from each other the higher the localization accuracy. However, as we increase the distance between each microphone pairs, we size of the overall array increases and the system becomes less portable. In the end we decided to build the two array system as described in fig~\ref{fig:sim_hm_2_array}. The setup is reasonably portable (compared to fig~\ref{fig:sim_hm_4}), yet it can achieve on average high localization accuracy within a region one meter by one meter close the setup. Since our target application is HCI, an one meter by one meter region will be adequate for this purpose and it will be used for all the following experiments.

>>>>

To avoid the need to accurately place microphones at far distances (as required by fig~\ref{fig:sim_hm_4}), we explored configuration with two arrays. Two $3$ microphone array are placed $1$ meter apart and the result is presented in fig~\ref{fig:sim_hm_2_array}.  The result indicates that this configuration has good accuracy when source is close to the arrays. We observe that the localization accuracy decreases as the sound source moves outside of the region one meter by one meter away from the two arrays. The average error is $2.60$ cm. \textcolor{red}{Generally, the clock used to sample microphone data has to be the same in order to compare arrival time differences. In the next Chapter, we will describe a method that does not require the clock to be synchronized across arrays. This approach would make the system easier to design since we don't need to consider clock synchronization issue}

@@

Looking at the simulation results on localization accuracy for different microphone array size and configurations, we see that the further away the microphones are placed from each other the higher the localization accuracy. However, as we increase the distance between each microphone pairs, the size of the overall array increases and the system becomes less portable. In the end we decided to build the two array system as described in fig~\ref{fig:sim_hm_2_array}. The setup is reasonably portable (compared to fig~\ref{fig:sim_hm_4}), yet it can achieve on average high localization accuracy within a region one meter by one meter close the setup. Since our target application is HCI, an one meter by one meter region will be adequate for this purpose and it will be used for all the following experiments.
